% (c) 2008 Sandesh Singh <sandesh247@gmail.com> http://sandesh247.com/
%
% Inspiration: resume by Matthew M. Boedicker <mboedick@mboedick.org> http://mboedick.org
%
\documentclass[a4paper,11pt,final]{article}

\usepackage{mdwlist}
\usepackage{url}

% font
\usepackage[T1]{fontenc}
\usepackage{tgpagella}

% \usepackage{lmodern}
\usepackage{marvosym}
%\usepackage[bitstream-charter]{mathdesign}
%\usepackage{gfsartemisia}
%\usepackage[urw-garamond]{mathdesign}
%\usepackage{fourier}
%\usepackage[adobe-utopia]{mathdesign}

%for windows fonts. use command xelatex
%\usepackage{fontspec}
%\fontspec[BoldFont={Gentium},BoldFeatures={Weight=4}]{Gentium}
%\setmainfont{Gentium Basic}

% \usepackage{oldstyle}

% save trees ;)
\usepackage{fullpage}
\usepackage{savetrees}

% meh ... me not a big fan of reduced linespread.
%\linespread{1}

% hyperlinks
\usepackage[pdftex,bookmarks=true,]{hyperref}
\hypersetup{
  pdftitle={Resume},    % title
  pdfauthor={Sandesh Singh},     % author
  pdfsubject={Resume},   % subject of the document
  pdfkeywords={keywords}, % list of keywords
  pdfnewwindow=true,      % links in new window
  colorlinks=false,       % false: boxed links; true: colored links
  linkcolor=red,          % color of internal links
  citecolor=green,        % color of links to bibliography
  filecolor=magenta,      % color of file links
  urlcolor=blue,          % color of external links
}
\urlstyle{same}

% \usepackage[open, openlevel=2]{bookmark}

% lighter bullets
\renewcommand{\labelitemi}{$\cdot$}

\raggedbottom

% custom commands
\newcommand{\resumetitle}[1]{%
  \subsection*{%
    \Large\sc{\textbf{#1}}%
    %\normalsize
  }%

  %\medskip%
}%

\newcommand{\jobexp}[5]{%
  \vspace{12pt}
  \noindent \textbf{{#4}}, \textbf{\href{#2}{#1}} \hfill \hbox{#3}
  \noindent {#5}
  \\\vspace{-12pt}
}

\newcommand{\projexp}[2]{%
  \vspace{12pt}
  \noindent\textbf{{#1}}
  \hfill
  \hbox{\textbf{{#2}}}
  \\ \vspace{-12pt}
}

\newcommand{\eduexp}[3]{%
\noindent\textbf{#1}\hfill{#2}\normalsize\\{#3}\vspace{3pt}%
}

\newcommand{\resumedescheader}[1]{%
  \bigskip
  \resumetitle{#1}
}%

%custom environments
\newenvironment{resumedescription}{%
  \begin{basedescript}{\desclabelstyle{\multilinelabel}\desclabelwidth{0.15\linewidth}}{%
      \renewcommand{\makelabel}[1]{{##1}}%
    }%
      \setlength{\itemsep}{0pt}
}{%
  \end{basedescript}%
}

\begin{document}

\pagestyle{empty}

\begin{center}
  \centering\Large\textbf{Sandesh Singh}\normalsize \\
  \centering{
    \makebox[0.3\linewidth][c]{
      \Mobilefone\hspace{1pt}
      +1 347-687-7748}
    \makebox[0.3\linewidth][c]{
      \Letter\hspace{1pt}
      \href{mailto:sandesh247@gmail.com}{me@sandesh247.com}
    }
    \makebox[0.3\linewidth][c]{
      \Keyboard\hspace{1pt}
      \url{http://sandesh247.com}
    }
  } \\
  \rule[2pt]{0.99\linewidth}{.1pt}
\end{center}

\vspace{-20pt}
\resumedescheader{Education}
\eduexp
	{Master's in Computer Science}
	{Expected Fall 2011}
	{GPA 4.0, Stony Brook University}
\\ \noindent \textbf{Courses}\quad Operating Systems, Analysis of Algorithms, Concurrent and Distributed Algorithms, Natural Language Processing, Computational Biology, Words and Pictures.
\\ \noindent \textbf{Master's Project}\quad Text mining for big-data analysis, under the advisement of Prof. Steven Skiena
\\
\vspace{-5pt}

\eduexp
	{Bachelor of Engineering (Computers)}
	{Jun 2006}
	{First Class, Vidyavardhini College of Engineering and Technology}
\\ \noindent \textbf{Courses} Artificial Intelligence, Advanced Databases, Operating Systems, Computer Networks

\resumedescheader{Skills}
\begin{resumedescription}
\item [Languages]
\begin{itemize*}
  \item Proficient in Java, Python, C\#, Javascript, Bash, C++
\end{itemize*}

\item [Data]
\begin{itemize*}
  \item Classification and mining with Weka, numpy, NLTK, learning R
  \item Data mining on Microsoft Analysis Services with MDX/DMX, SQL
\end{itemize*}

\item [Cloud]
\begin{itemize*}
  \item Google AppEngine applications, using webpy and Django
  \item Amazon EC2 for distribution (via Hadoop)
\end{itemize*}

\item [Frameworks]
\begin{itemize*}
  \item OR Mapping frameworks (NHibernate, Microsoft Entity Framework, Gentle.Net)
  \item Social frameworks (GData Python Client, Facebook applications)
  \item Web frameworks (ASP.Net, Django, Google AJAX API, jQuery)
\end{itemize*}

\end{resumedescription}

%% \vspace{-7pt}
%% \resumedescheader{Academic Projects}
%% \begin{itemize*}
%%   \item implemented and tested new \textbf{text classification algorithms} in the Applied Logic Lab.
%%   \item worked on a \textbf{classifier to detect vandal edits} on wikipedia (84\% precision, 89\% recall)
%%   \item developed a system to \textbf{recognize the language of a
%%     speaker from audio} (9 languages, 72\% precision, 73\% recall);
%%     currently working under Prof. Steven Skiena towards improving and
%%     extending the system
%%   \item developed a highly-available, concurrent mail server in Java, extensible through web-services
%%   \item conducted workshops \& seminars on various topics, including databases, programming and graphics
%%     %\item developed a book exchange site, where students could request for and put up books for lending
%%     %\item was the college web-master, maintained the website and on-line registrations for various events
%% \end{itemize*}

\vspace{-15pt}
\resumedescheader{Career}

\vspace{-12pt}

\jobexp {Kindle Team, Amazon Inc.}
  {https://kindle.amazon.com/}
  {May 2011 - August 2011}
  {Software Developer Intern}
  {Improved the Kindle experience by understanding user behavior using machine learning}

\jobexp	{Neorithm Technologies}
	{http://www.neorithm.com}
	{Oct 2008 - July 2010}
	{Technical Leader}
	{Core team member since inception, led the technology R\&D across the company's product lines}
%% \begin{itemize*}
%% \item core team member since inception, I \textbf{led the technology R\&D} across the company's product lines
%% em built a rule engine to filter `interesting' transactions in a bank, which led to an \textbf{anti money laundering} product currently deployed in a bank
%% em developed a \textbf{business intelligence} product, where a financial institutions' relational data is imported into a SSAS cube, and analyzed in a pivot table built in Flex
%% em developed a C\# API to emulate a \textbf{versioned filesystem}, with pluggable storage support; in particular, a file--system and a relational database back--ends are ready
%% em oversaw the development of a \textbf{loan origination system}, where potential customers were identified and clustered based on various financial, demographic and personal parameters
% \item undertook \textbf{consulting assignments} on behalf of neorithm for performance optimization
%% \end{itemize*}

\jobexp {Finacus Solutions}
	{http://www.finacus.com}
	{Nov 2007 - Aug 2008}
	{Senior Software Engineer}
	{Core team member, enabled rapid application development with an in-house framework}
%% \begin{itemize*}
%% \item developed an \textbf{enterprise application development framework}, consisting of workflows, an ORM framework, message queues; and code generators for an ASP.Net based UI
%% \item assisted in the development of an \textbf{ATM switch}, supporting the Diebold and NCR protocols
%% \item played a major role in improving the \textbf{usability} of web applications, using JavaScript to bring desktop--like features to web applications
%% \end{itemize*}

\jobexp {Amdocs Development Center (India)}
	{http://www.amdocs.com}
	{Aug 2006 - Oct 2007}
	{Subject Matter Expert}
	{Implemented Amdocs' telecom billing functionality using Unix processes}
%% \begin{itemize*}
%% \item worked on extending the functionality of Amdocs' `\textbf{Rater}' product for two successive versions, writing \textbf{shell scripts and C++ daemons} on Unix (Sun and AIX) systems
%% \item traveled to Israel for testing, and to Russia for production support of `Rater' deployment
%% \end{itemize*}

\resumedescheader{Papers and publications}
\begin{itemize*}
\item Language of Vandalism: Improving Wikipedia Vandalism Detection via Stylometric Analysis --- \textbf{ACL 2011}
\item Domain Independent Authorship Attribution without Domain Adaptation {\small\textbf{(presenter only)}} --- \textbf{RANLP 2011}
\item Filed for a patent on techniques used at Amazon during internship
%% \item Technical adviser and webmaster for the student's chapter of the
%%  Computer Society of India
%% \item Received accolades and cash bonuses while working in Amdocs DVCI
%% \item Listen to Hans Zimmer, ColdPlay, Amanda Palmer; read
%%  P.G. Wodehouse, John Grisham; play cricket
\end{itemize*}

\resumedescheader{Projects}

\vspace{-12pt}
\projexp{Vandalism detection in
  Wikipedia}{Stony Brook University}

\noindent Hypothesised and validated an NLP approach to detecting
vandalism, by modeling good and vandal edits using a probabilistic
context free grammar, and evaluating new edits, attaining 84\%
precision and 89\% recall.

\projexp{Pattern recognition in human speech}{Stony Brook University}

\noindent Built a classifier to detect the language of a human
speaker, by building an ngram model over various features of an audio
signal. The classifier attained an accuracy of 72\% and recall of
73\%, when tested over 9 languages.

\projexp{Language detector for textual data}{Stony Brook University}

\noindent Implemented a novel algorithm, under the guidance of Yuri
Puzis, to \textbf{detect the language of a given piece of text using a
  trie based decision tree}. The accuracy of the classification could
be increased to an arbitrary level -- limited by a dictionary -- while
training the decision tree.

\projexp{Social network based on recommendation}{Self and friends}

\noindent Built a \textbf{recommendation based social network on the
  Google AppEngine}, using Django. Given things one likes and doesn't
like, people whose likes were most similar were matched up.

\projexp{Differential AJAX Server}{Neorithm Technologies}

\noindent \textbf{Modified the ASP.Net pipeline to AJAX-ify legacy
  ASP.net applications}, based on the `diff' of the pages being
transmitted to the client. Built custom modules such that the server
would only hand out a diff of the new page with respect to the older
page, and an injected javascript on the client would merge the
changes.

\projexp{Optimized MDX query generator}{Neorithm Technologies}

\noindent Developed a \textbf{translator to generate an optimized MDX
  query} for a given high level declarative user query in XML, which
was used to query a Microsoft Analysis Services OLAP warehouse. This
was part of an Anti-Money Laundering product, whose development I led.

\projexp{Versioned file storage engine}{Neorithm Technologies}

\noindent Developed a \textbf{datastore to store files}, and exposed
an API in C\#. The datastore had versioning support, and supported
multiple implementations for actual storage of files. In particular, a
file-system based, and a relational database backends were built.

\projexp{ATM switch}{Finacus Technologies}

\noindent Built a \textbf{daemon to run on ATMs, and carry out
  transactions with banks} using the Diebold and NCR protocols. The
daemon was written using the Microsoft.Net framework and was
extensible to support other protocols.

\projexp{Web application development framework}{Finacus Technologies}

\noindent Built a \textbf{web application development framework}, consisting of
UI elements in the form of ASP.net controls, an ORM, workflows and
code generators. These greatly reduced the development time and
provided independence from 3rd party vendors.

\projexp{\textit{Rater} extensions}{Amdocs}

\noindent Developed various daemons and C++ extensions to support the
telecom billing processes of Amdocs' \textit{Rater} product, on Sun
Sparc and AIX systems. Also traveled to Israel and Russia for
testing and production support.

\projexp{The Distributed DataBase}{Vidyavardhini College of
  Engineering}

\noindent Developed the parser, query execution engine and GUI for
\textbf{T}he \textbf{D}istributed \textbf{D}ata\textbf{B}ase
(\url{http://tddb.sf.net}), \textbf{a true distributed database built
  from the ground up}, which conforms to the SQL-92 syntax.

\projexp{Email Server}{Vidyavardhini College of Engineering}

\noindent Built an email server in JSP/servlets, where the
communication between the server and client was done through web
services.

\projexp{Wordlist trainer}{Self}

\noindent Built a web application \url{http://wl.sandesh247.com} to
help students prepare for wordlists for exams like the GRE. It uses an
\textbf{AJAX interface which communicates with the backend using a
  REST-api}, and has unique approach to learning - \textit{revise that
  which you did not know the last time}, taking out the tedium to
manually mark ``hard'' words.

\projexp{Various jQuery plugins}{Self}

\noindent Built various \textbf{jQuery plugins} during the course of
my employment in Neorithm Technologies, while improving usability in
web applications. Some of them can be seen in online repositories
linked at the end of this resume.

%\resumedescheader{Academic Experience}

\resumedescheader{Links}
\begin{itemize*}
\item  Code samples: \url{http://github.com/sandesh247}; \url{http://code.google.com/u/sandesh247}
\item  Blog: \url{http://sandesh247.com/journal}
\end{itemize*}

\end{document}

